An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2024-10-02 article_with notes.tex
discussion

Strong demands for Australian wine have historically helped to create a thriving industry. However, recent pressures brought on by a loss of tourism and labour due to the COVID-19 pandemic, the global freight crisis, war in Europe, tariffs and rising inflation have negatively affected the industry's outlook \citep{wineaustraliaNationalVintageReport2021,wineaustraliaAustralianWineProduction2021}. The 2021-2022 financial year alone saw a decline of 19\% in exports solely due to tariffs \citep{wineaustraliaNationalVintageReport2022}. A greater understanding of the different underlying conditions leading to improved performance in agricultural productivity and sustainability at scale is key to making data-informed decisions to increase a nation's agricultural sustainability \citep{oecdInnovationProductivitySustainability2019}. Specifically within the Australian wine and vine industry, there is a need to further understand the driving relationships between resource use and economic output, which can help to determine more cost effective, efficient methods, and to develop benchmarks with local growers \citep{lukemanciniUnderstandingAustralianWine2020}.

@@

This study is further driven by recent reveiews calling for data-driven studies to show the economic benefits of sustainable practices within the wine industry, specifically winegrowing. While there is evidence to suggest that environmentally sustainable pracitces can reduce costs, increase efficiency, and improve the quality of grapes, more research is needed to numerically demonstrate these benefits across different regions and climates #TODO:(Baiano, 2021; Mariani and Vastola, 2015; Montalvo-Falcón et al., 2023). Futhermore, many different sustainable approaches exist but are often studied in isolation or are limited in their geographical and climatic conditions, restricting their generalisability. We embrace the variation that exists between vineyards and their unique challenges across Australia. Where, vineyard decisions on-the-ground are governed by complex physical forces of a regions' resources, climate, soil and geology, as well as by external pressures such as international market demands, disease and natural disasters (Abad et al., 2021; Cortez et al., 2009; Hall et al., 2011; I. Goodwin, et al., 2009; Kasimati et al., 2022; Oliver et al., 2013; Srivastava and Sadistap, 2018).

@@

% TODO:

@@

XGBoost is an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function to create new decision trees that add to the ensemble, improving its predictive power. The loss function is optimised iteratively to improve upon prior trees (where the loss function can be any convex function), allowing gradient descent to traverse the loss space until no substantive improvements can be made (further detail pertaining to the algorithm is described in the Appendix). Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting. This makes XGBoost incredibly versatile and accurate, whilst still being interpretable compared to other machine learning methods (TODO: ref).
XGBoost analyses were conducted using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. It is a method that is widely used within agriculture for yield prediction (TODO: ref), but is also highly capable method for financial predictions, even when dealing with multi-domain predictor variables (TODO: ref). We utilise XGBoot due to a combination of agricultural yield prediction, financial prediction and the use of both economic and environmental variables as XGBoost is known to perform well with mixed types of predictor domains (TODO: ref). Furthermore we choose XGBoost as it has a good performance in predictions whislt allowing the use of directly comparable metrics to sanity check models against prior research (such as yield using $R^2$), offering insight into the relative performance of models lacking prior reference points in the literature such as revenue and operating costs and making the model more interpretable to audiences familiar with regression models. 

@@

The ability to classify and predict continuous response variables and categoric variables alongside one another was also a consideration in the use of XGBoost, as both were contained in the data. XGBoost was also used due to its ability to handle sparse data, which was present within this dataset due to the voluntary nature of data entry, with many fields being left blank during data collection. Tree based methods also do not require data to be transformed prior to analyses; this consideration was taken into account so that specific partitions of values could be evaluated more easily and understood within original units of the data (TODO: ref). A further consideration in its use was the level of interpretability offered through measures of 'relative importance' allowing for the ability to identify and rank variables and interactions by contribution to predictions \citep{chenXGBoostScalableTree2016}.

@@

An XGBoost model was trained for each variable so that every variable's relative importance could be caculated. This process was done three times using three iterations of data (three models for each variable). The first models were trained on the original SWA data set, the second were trained on a dataset that incorporated external data for each region (see TODO: insert a table for this) and the final were trained on data with continuous variables transformed to be expressed as a ratio of vineyard area. The final dataset that consisted of ratios also included the extra regional data (but not in ratio form).

\subsection{Sankey and Chord Diagrams}
Originally created by Sankey to depict different pressures in steam engines (TODO: ref) we leverage Sankey diagrams to illustrate the different impact or 'pressure' each variable has on one another through the use of measurements of variable importance. Sankey and Chord diagrams were constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Sankey diagrams (depicted on the left as section A in figures) show the top 10 contributing factors to a variables prediction using XGBoost and Chord diagrams, a circular represntation of Sankey diagrams (depicted on the right as section B in figures) show how each of the top 10 factors relate to one another by measures of relative importance. Both Chord and Sankey diagrams illustrate variable importance through the size of the bands between two variables. The number at the end of a connection in the diagrams indicates a variabless importance (the number of times it appeared within the ensemble).

@@

As part of the utilising the XGBoost model the hyperparameters of the model were tuned. The XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. This allowed us to utilise cross validated grid search functions when selecting for better performing hyperparameters. This method required three distinct types of metrics to be used for the three types of variables incorporated into the analysis (multiclass, binary and numeric). For consistency the metrics utilised by the grid search were aligned with the error functions used when training the model on those variables. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for binary variables \citep{hanley1982meaning}. And, multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

@@

The predictive performance of the XGBoost model for revenue performed similarly to operating cost, for achieving an $R^2$ of 0.77 (with a standard deviation of 0.15). 
\par
The most important predictors of revenue were fuel use (petrol 307 and diesel 144), yield (285), size (216) and water use (199). The values attached to each variable indicate the relative importance of the variable (number of times selected in the tree ensemble, see Section \ref{fig:revenue_sankey}). Overall regions contributed to 234 nodes in the ensemble making them collectively the third most important variable. The chord diagram (see Figure \ref{fig:revenue_sankey}) illustrates that vineyard area is also of high relative importance to other variables, especially slashing. The overall importance of Area to other variables is evident by its larger circumference within the chord diagram.
% The strong relationship of vineyard area to revenue and its predictors  but also has a high relative importance to the other predictors, The relation to area is likely to primarily be the effect of economies of scale, shown through its strong relations to other variables in figure \ref{fig:revenue_sankey}. Area harvested is likely also an indicator of other variables such as slashing passes its strongest connection presented.

@@

% \begin{figure} 
%   \resizebox{\textwidth}{!}{
%   \includegraphics{operating_costs.pdf}}
%   \caption{A surrogate model decision tree predicting operating costs. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:operating_tree}
%  \end{figure}

Compared to revenue, the predictive performance of the XGBoost model for operating cost was slightly better, with an $R^2$ of 0.80 (with a standard deviation of 0.10). Similar to revenue, the most important predictors of operating cost were fuel, water, area and yield (see figure \ref{fig:operating_costs_sankey}). A surprising difference was the change in relative importance of activities involving tractor passes where the use of fungicide was more important for operational costs, compared to revenue, where slashing was more important (see Figure \ref{fig:region_sankey}). The connection between spraying and operational costs is intuitive in that it utilises equipment and resources to do. However, it is surprising that although spraying is considered important, that area not harvested due to disease is not, even though this would be a direct cause. The lack of importance on disease directly could be because of a low amount disease reported in the dataset (137 vineyards). The use of spraying is also unfortunately not part of the data, and could be in response to a variety of factors such as other vineyards within the region having disease or preventative sprays. The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.

@@

Although region plays a strong role, it was found that factors that can be considered regionally important were not always rated high in relative importance. This was noted especially when considering oversimplified models, such as the obvious partitioning of river water as the primary source of water to identify vineyards located in the riverland (with 456 of 472 vineyards in the riverland utilising riverwater). The occurence of factors dominated by particular practices also washes out the ability to determine the effects of practices and their benefits that are widely used by this sample of vineyards. A keen example is the use of techniques such as cover crops and their prevalance within the sample, where just over 85\% (5272) of vineyards utilised some form of cover crop such as grassing and only just under 4\% (225) used only bare soil (with the remaining 552 utilising a combination). The high percentage of vineyards using this type of sustainable practice means that its effect is will not be prominent within the model, and can only show what practices would further improve those already implementing these techniques, and how they are connected to these operating costs. A strength of utilising XGBoost in this context is that, a subset of particular interest can be leveraged to focus in on the combination of factors that would contribute to the specific concieved scenario.

@@

\subsection{Yield}

@@

  \includegraphics{region.png}}
  \caption{The left-hand side, A,  depicts the 10 most relative important variables in predicting Region using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:region_sankey}

@@

% Cover crops are an example of a sustainable practice in viticulture in which the area between vine rows is seeded with a crop such as grasses or native vegetation. The primary reason for employing cover crops is to reduce the presence of disease and weeds (Delpuech and Metay, 2018). The benefit of reducing diseases and weeds is especially notable, as there is less cause to utilise heavy machinery for spraying herbicides and fungicides, or for mechanical weeding (Capello et al., 2019). The presence of a cover crop can also help to increase soil water retention, reducing erosion and water runoff in shallow soils, having been shown to mitigate runoff during rain events by over 65% (Capello et al., 2020). However, cover crops can introduce competition with grapevines and may reduce yield depending upon the plants used and the density of the cover crop (Capello et al., 2019; Delpuech and Metay, 2018; Gosling and Shepherd, 2005; Monteiro and Lopes, 2007). A coverage of only 30% is required to provide protection against erosion, yet increased cover provides the benefits of greater biodiversity at the risk of yield (Delpuech and Metay, 2018).
% The reduction of tillage operations through optimising tractor efficiency is another practice that reduces energy use in vineyards, decreasing running costs, as well as reducing soil compaction (Capello et al., 2019). An increase in soil compaction has been shown to increase water runoff (Capello et al., 2020). Runoff is a significant factor as extreme rain events can cause large scale soil deposition, creating further erosion and removing topsoil. It is important that the interaction of events such as erosion have on other considerations such as soil health. 

@@

This study explored the relationships between vineyard resource use, operations and geographical properties to revenue and operating costs. The analysis was based on a large national study of 6049 samples collected over ten years. Three main findings were identified. First, the most important predictors of revenue and operating costs were fuel, yield and area. Secondly, area and fuel were highly interrelated to other variables (see Figure \ref{fig:operating_costs_sankey} and Figure \ref{fig:revenue_sankey}A). Finally, the relative importance of predictor variables for Region, differed from Revenue and Operating costs, with Water Use being more prominent than Yield. Region was also more prominent than illustrated in the Sankey diagrams due to the relative importance for operating cost and revenue being calculated for individual regions and not all regions together. In its entirety Region was the third most important predictor of revenue and the most important predictor for operating costs, relative to the other variables consideration in the analyses.

@@

Several physical parameters such as climate, geography and soil are predetermined by a vineyard's location, making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}.
The association between yield and region is demonstrated by yield apparing as the fourth most important variable when determining region (see Figure \ref{fig:region_sankey}).
% The association with area and region is likely a connection to the change in land costs, with inland Australian areas (particularly of lower rainfall) being substantially cheaper to buy than coastal regions, allowing larger areas to be purchased \citep{willchancellorMeasuringAustralianBroadacre2019} % TODO: This section is commented out due to Mardi's take:
%  Maybe but not sure this assumption holds. It may be an artefact of the members being corporate in larger holdings. The larger percentage of blocks in the riverland are small.

@@

Warmer regions are known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of grapes; reflected through region using water use so prominently in the XGBoost ensemble. The link to water resources in defining regions is also an important consideration, as vineyards can leverage higher irrigation rates if water resources are available. A further consideration in the link between revenue and region is that grape prices are set at a regional level by buyers \citep{wineaustraliaNationalVintageReport2022}. It is also important to consider that some regions carry particular fame regarding the quality of their produce such as Tasmania, the Hunter Valley and Barossa Valley \citep{hallidayAustralianWineEncyclopedia2009}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}.

@@

When determining revenue, similar variables were used to operational cost; with region also being of high variable importance relative to other variables (when considering all regions together in importance). It is difficult to extrapolate the specific influence of location on a vineyard's outcomes due to the broad and varying definition of a region. Utilising the Geographical Indicator regions defined by Wine Australia \citep{wineaustraliaWineAustraliaOpenData2021} is a limitation in one way, as it is too broad to fully capture a vineyards location and how that influences variables at a more granular level. However, as buyers set prices at regional levels, it is still important to consider this factor. 

>>>>

Strong demands for Australian wine have historically helped to create a thriving industry. However, recent pressures brought on by a loss of tourism and labour due to the COVID-19 pandemic, the global freight crisis, war in Europe, tariffs and rising inflation have negatively affected the industry's outlook \citep{wineaustraliaNationalVintageReport2021,australiaAustralianWineProduction2021}. The 2021-2022 financial year alone saw a decline of 19\% in exports solely due to tariffs \citep{wineaustraliaNationalVintageReport2022}. A greater understanding of the different underlying conditions leading to improved performance in agricultural productivity and sustainability at scale is key to making data-informed decisions to increase a nation's agricultural sustainability \citep{oecdInnovationProductivitySustainability2019}. Specifically within the Australian wine and vine industry, there is a need to further understand the driving relationships between resource use and economic output, which can help to determine more cost effective, efficient methods, and to develop benchmarks with local growers \citep{lukemanciniUnderstandingAustralianWine2020}.

@@

This study is further driven by recent reveiews calling for data-driven studies to show the economic benefits of sustainable practices within the wine industry, specifically winegrowing. While there is evidence to suggest that environmentally sustainable pracitces can reduce costs, increase efficiency, and improve the quality of grapes, more research is needed to numerically demonstrate these benefits across different regions and climates \citep{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023, laurentReviewIssuesMethods2021}. Futhermore, many different sustainable approaches exist but are often studied in isolation or are limited in their geographical and climatic conditions, restricting their generalisability. We embrace the variation that exists between vineyards and their unique challenges across Australia. Where, vineyard decisions on-the-ground are governed by complex physical forces of a regions' resources, climate, soil and geology, as well as by external pressures such as international market demands, disease and natural disasters \citep{abadCoverCropsViticulture2021,cortezUsingDataMining2009,goodwinijeriepRegulatedDeficitIrrigation1992,hallSeasonTemporalVariation2011,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNonDestructiveSensingMethods2018}.

@@

@@

XGBoost is an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function to create new decision trees that add to the ensemble, improving its predictive power. The loss function is optimised iteratively to improve upon prior trees (where the loss function can be any convex function), allowing gradient descent to traverse the loss space until no substantive improvements can be made (further detail pertaining to the algorithm is described in the Appendix). Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting. This makes XGBoost incredibly versatile and accurate, whilst still being interpretable compared to other machine learning methods \citep{kistenExplainableArtificialIntelligence2024}.

@@

XGBoost analyses were conducted using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. It is a method that is widely used within agriculture for yield prediction \citep{d.mariadassExtremeGradientBoosting2022,liGlobalDetrendingSignificantly2024,raviCropYieldPrediction2020}, but is also highly capable method for financial predictions, even when dealing with multi-domain predictor variables \citep{ZHANG2023104045}. We utilise XGBoot due to a combination of agricultural yield prediction, financial prediction and the use of both economic and environmental variables as XGBoost is known to perform well with mixed types of predictor domains \citep{doi:10.1080/15481603.2024.2349341,ZHANG2023104045}. Furthermore we choose XGBoost as it has a good performance in predictions whislt allowing the use of directly comparable metrics to sanity check models against prior research (such as yield using $R^2$), offering insight into the relative performance of models lacking prior reference points in the literature such as revenue and operating costs and making the model more interpretable to audiences familiar with regression models \citep{heFruitYieldPrediction2022,laurentReviewIssuesMethods2021}.

@@

The ability to classify and predict continuous response variables and categoric variables alongside one another was also a consideration in the use of XGBoost, as both were contained in the data. XGBoost was also used due to its ability to handle sparse data, which was present within this dataset due to the voluntary nature of data entry, with many fields being left blank during data collection. Tree based methods also do not require data to be transformed prior to analyses; this consideration was taken into account so that specific partitions of values could be evaluated more easily and understood within original units of the data \citep{d.mariadassExtremeGradientBoosting2022}. A further consideration in its use was the level of interpretability offered through measures of 'relative importance' allowing for the ability to identify and rank variables and interactions by contribution to predictions \citep{chenXGBoostScalableTree2016}.
An XGBoost model was trained for each variable so that every variable's relative importance could be caculated. This process was done three times using three iterations of data (three models for each variable). The first models were trained on the original SWA data set, the second were trained on a dataset that incorporated external data for each region and the final were trained on data with continuous variables transformed to be expressed as a ratio of vineyard area. The final dataset that consisted of ratios also included the extra regional data (but not in ratio form).

\subsection{Sankey and Chord Diagrams}
Originally created by Sankey to depict different pressures in steam engines \citep{7536189} we leverage Sankey diagrams to illustrate the different impact or 'pressure' each variable has on one another through the use of measurements of variable importance. Sankey and Chord diagrams were constructed using the Holoviews python library \citep{rudigerHolovizHoloviewsVersion2020}. Sankey diagrams (depicted on the left as section A in figures) show the top 10 contributing factors to a variables prediction using XGBoost and Chord diagrams, a circular represntation of Sankey diagrams (depicted on the right as section B in figures) show how each of the top 10 factors relate to one another by measures of relative importance. Both Chord and Sankey diagrams illustrate variable importance through the size of the bands between two variables. The number at the end of a connection in the diagrams indicates a variabless importance (the number of times it appeared within the ensemble).

@@

As part of the utilising the XGBoost model the hyperparameters of the model were tuned. The XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. This allowed us to utilise cross validated grid search functions when selecting for better performing hyperparameters. This method required three distinct types of metrics to be used for the three types of variables incorporated into the analysis (multiclass, binary and numeric). For consistency the metrics utilised by the grid search were aligned with the error functions used when training the model on those variables. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for binary variables \citep{hanleyMeaningUseArea1982}. And, multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

@@

There was little difference in predictive power between the inclusion of climatic and regional data and the use of region alone. With the use of extra regional data achieving an $R^2$ of 0.76 (with a standard deviation of 0.13), and when not using the extra regional data achieving an $R^2$ of 0.77 (with a standard deviation of 0.15). The higher number of variables included as part of the regional data likely resulting in a lower variance in predictive power when including the extra regional data.
\par
The most notable difference was in the importance of the predictors, where elevation was a had a high relative importance of 8, only surpassed by diesel and yield, with 9 and 45 relative importance respectively (TODO: see figure). The lower variance is also reflected in the lower amount of nodes (or partitions) required when leveraging the extra regional parameters, with a reduction in hundreds of splits between the two models. Without the extra regional parameters it was found that fuel use (petrol 307 and diesel 144), yield (285), size (216) and water use (199) held the highest relative importance (TODO: see figure).
\par
Even without the extra regional parameters, overall region contributed to 234 nodes in the ensemble making it collectively the third most important variable. This places equal importance within both models on region however the nature of regions contribution is more generalised using elevation when included as a parameter. This alone does not necessarily make elevation a direct contributing factor but links regions that of similar terrain together. The relevance of this was noted when reviewing regional missclassifications, where neighbouring regions were often misclassified as each other. The extra numerical parameters that can be partitioned likely gives the algorithm a greater ability to partition these regions together using fewer nodes.
% The strong relationship of vineyard area to revenue and its predictors  but also has a high relative importance to the other predictors, The relation to area is likely to primarily be the effect of economies of scale, shown through its strong relations to other variables in figure \ref{fig:revenue_sankey}. Area harvested is likely also an indicator of other variables such as slashing passes its strongest connection presented.

@@

% \begin{figure} 
%   \resizebox{\textwidth}{!}{
%   \includegraphics{operating_costs.pdf}}
%   \caption{A surrogate model decision tree predicting operating costs. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:operating_tree}
%  \end{figure}
Compared to revenue, the predictive performance of the XGBoost model for operating cost was slightly better when not using the extra regional parameters, with an $R^2$ of 0.80 (with a standard deviation of 0.10). Similarly, when predictin without extra regional data the most important predictors of operating cost were fuel, water, area and yield (see figure \ref{fig:operating_costs_sankey}).
A major difference was also in the poorer performance of the model with extra regional parameters. Although achieving a similar $R^2$ of 0.78 and a standard deviation of 0.12 the difference lay in an outlier model recording an $R^2$ of 0.08. This divergence likely being due to over generalising using elevation to match neighbouring regions. The removal of this radical leaves the inclusion of extra regional parameters outperforming the models without them, however it overlooks the major pitfall in the ease of misattributing factors and causality when predicting these variables.
A surprising difference between operating cost and revenue was the change in relative importance of activities involving tractor passes where the use of fungicide was more important for operational costs, compared to revenue, where slashing was more important (see Figure \ref{fig:region_sankey}). This difference was only found when not including the extra regional parameters. The model including extra regional parameters reflected an identical hierarchy of importance to its revenue counter part (TODO: see figs).
The connection between spraying and operational costs is intuitive in that it utilises both the expense of equipment and resources. However, it is surprising that although spraying is considered important when extra regional paramters were not included, 'area not harvested due to disease' was not, even though disease would be a direct cause. The lack of importance on disease directly could be due to a low amount reported in the dataset (137 vineyards). The reason for spraying was also unfortunately not part of the data, and could be in response to a variety of factors such as other vineyards within the region having disease or preventative sprays. The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.

@@

@@

@@

\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{region.png}}
  \caption{The left-hand side, A,  depicts the 10 most relative important variables in predicting Region using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:region_sankey}
 \end{figure}

\subsection{Results per hectare}
Both operating cost and revenue were predicted as ratios of area (revenue and operating cost per vineyard hectare). In both cases it was found that the models performed poorly with operating costs recording an $R^2$ of 0.24 (with a standard deviation of 0.15) and revenue an $R^2$ of 0.32 (with a standard deviation of 0.14).

@@

The significance of yield and region is demonstrated by their continual apparance as important variables when predicting operating costs and revenue. Several physical parameters such as climate, geology and soil are predetermined by a vineyard's location, making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. The relationships between vineyard resource use, operations and geographical properties is a complex one, illustrated through the highly interelated properties demonstrated in the chord diagrams. The difference in resources available between regions is well illustrated when considering the relative importance that water use had in predicting region. The difference in readily available resources between different regions is also easily demosntrated when observing the partitioning of river water as the primary source of water to identify vineyards located in the riverland (with 456 of 472 vineyards in the riverland utilising riverwater).
The availability of resources and geographical features of a region are significant but are also a potentially determining factor in the types of operational decisions made, and thus the reasoning as to variation in revenue and operating costs. This can be seen in the addition of extra regional paramters that add greater context to understanding the why or cause of operating costs and revenue. The effect of different operational consideration can be reflected in higher costs likely incurred in regions of greater variations in slope requiring more specialised equipment, or reflected in the types of resources available in some regions. The specifics of a vineyards' site are of incredible importance when determining what causes higher operational costs or revenue. Although it is useful to be able to predict and compare regions and their revenue and operational costs, a greater nuace to help understand the why behind these decisions, would help in specifically guiding operational decisions. AN example of this can is whether the reduction of tillage operations through optimising tractor efficiency would be useful and how to optimise tractor use for a specific operation. This example is chosen as while this practice is undertaken to reduce energy use in vineyards, decreasing running costs, as well as reducing soil compaction (Capello et al., 2019). The interrelatedness of this decisions is far reaching as increase in tractor use can cause soil compaction which has been shown to further increase water runoff (Capello et al., 2020). With runoff itself being a significant factor during extreme rain events which can lead to large scale soil deposition, creating further erosion and removing topsoil and having wide spread effects for a vineyard. 
% Differences between regions also likely extends further to the types of employed methods and the reason for using them.
% An important and ongoing consideration for vineyards that changes with location is soil, which interacts with every other practice in various ways at different time scales. The inclusion of soil specifically within this model was not possible but For example, cover crops have been shown to be detrimental for soil health in the short term, giving an initial reduction in soil potassium and phosphorus concentrations and no change in nitrogen levels (Gosling and Shepherd, 2005). Conversely, in longer time frames the presence of a cover crop can induce an increase in microorganisms, which can excrete phosphates and potassium, regenerating the soils chemical balance and helping to introduce further organic nitrogen (Coll et al., 2011). 

@@

@@

Further to the consideration of including specific operations is hindered in this model due to the sample being derived specifically from vineyards already within a sustainable program. Making the sample inherintly biased towards the use of sustainable practices. A keen example is the use of techniques such as cover crops. Cover crops are an example of a sustainable practice in viticulture in which the area between vine rows is seeded with a crop such as grasses or native vegetation. The primary reason for employing cover crops is to reduce the presence of disease and weeds (Delpuech and Metay, 2018). The benefit of reducing diseases and weeds is especially notable, as there is less cause to utilise heavy machinery for spraying herbicides and fungicides, or for mechanical weeding (Capello et al., 2019). The presence of a cover crop can also help to increase soil water retention, reducing erosion and water runoff in shallow soils, having been shown to mitigate runoff during rain events by over 65\% (Capello et al., 2020). However, cover crops can introduce competition with grapevines and may reduce yield depending upon the plants used and the density of the cover crop (Capello et al., 2019; Delpuech and Metay, 2018; Gosling and Shepherd, 2005; Monteiro and Lopes, 2007). A coverage of only 30\% is required to provide protection against erosion, yet increased cover provides the benefits of greater biodiversity at the risk of yield (Delpuech and Metay, 2018). The presence of cover crops within the sample is reflects this bias, where just over 85\% (5272) of vineyards utilised some form of cover crop such as grassing and only just under 4\% (225) used only bare soil (with the remaining 552 utilising a combination). The high percentage of vineyards using this type of sustainable practice means that its effect is will not be prominent within the model, and can only show what practices would further improve those already implementing these techniques, and how they are connected to these operating costs. A strength of utilising XGBoost in this context is that, a subset of particular interest can be leveraged to focus in on the combination of factors that would contribute to the specific concieved scenario.

@@

Warmer regions are known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{bottingCanopyArchitectureImplicationsShiraz1996}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of grapes; reflected through region using water use so prominently in the XGBoost ensemble. The link to water resources in defining regions is also an important consideration, as vineyards can leverage higher irrigation rates if water resources are available. A further consideration in the link between revenue and region is that grape prices are set at a regional level by buyers \citep{wineaustraliaNationalVintageReport2022}. It is also important to consider that some regions carry particular fame regarding the quality of their produce such as Tasmania, the Hunter Valley and Barossa Valley \citep{hallidayAustralianWineEncyclopedia2009}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}.

@@

When determining revenue, similar variables were used to operational cost; with region also being of high variable importance relative to other variables (when considering all regions together in importance). It is difficult to extrapolate the specific influence of location on a vineyard's outcomes due to the broad and varying definition of a region. Utilising the Geographical Indicator regions defined by Wine Australia \citep{australiaWineAustraliaOpenData2021} is a limitation in one way, as it is too broad to fully capture a vineyards location and how that influences variables at a more granular level. However, as buyers set prices at regional levels, it is still important to consider this factor. 
